---
title: Analysis of the effect of speaking style on speech segmentation by statistical
  learning
output:
  html_document: default
  pdf_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Load packages
```{r message=FALSE, warning=FALSE}
library(ggplot2)
library(ggbeeswarm)
library(readxl)
library(plyr)
library(dplyr)
library(brms)
library(bayesplot)
library(tidyr)
library(tidybayes)
```

```{r include=FALSE}
# Run this to load all objects saved in the RData file, so that there is no need to run the whole code again
load("all_objects.RData")
```

# Load data
```{r}
dat1 <- read_xlsx('/Users/adamguo/Desktop/Data analysis/data.xlsx')
```

# Data preprocessing
## 1. Exclude timeouts
```{r}
# Exclucde timeouts (i.e., no responses)
dat2 <- dat1[!is.na(dat1$Response), ]
print(paste("No. of trials excluded:", nrow(dat1) - nrow(dat2)))
```

## 2. Exclude outliers
```{r}
# Outliers: subjects with accuracy 2 SDs below the mean of their condition

# Calculate individual subjects' accuracy
acc_by_sub <- aggregate(Accuracy ~ Subject + Condition, dat2, mean)

# Compute SD and mean for each condition
cond_sd <- aggregate(Accuracy ~ Condition, acc_by_sub, sd)
cond_mean <- aggregate(Accuracy ~ Condition, acc_by_sub, mean)

# Append SD and mean values to the dataframe acc_by_sub
acc_by_sub <- merge(cond_sd, acc_by_sub, by = c("Condition"))
acc_by_sub <- merge(cond_mean, acc_by_sub, by = c("Condition"))

# Rename the dataframe columns
names(acc_by_sub)[names(acc_by_sub) == "Accuracy"] <- "Mean"
names(acc_by_sub)[names(acc_by_sub) == "Accuracy.x"] <- "SD"
names(acc_by_sub)[names(acc_by_sub) == "Accuracy.y"] <- "Accuracy_sub"

# Compute the exclusion threshold (2 SDs below the mean)
acc_by_sub$Lower_bound <- acc_by_sub$Mean - 2 * acc_by_sub$SD

# Subjects who are outliers:
outliers <- acc_by_sub$Subject[acc_by_sub$Accuracy_sub < acc_by_sub$Lower_bound]
outliers
```

```{r}
# Now, exclude them from the data
dat3 <- dat2[!dat2$Subject %in% outliers, ]

print(paste("No. of trials excluded:", nrow(dat2) - nrow(dat3)))
```

# Prepare for analysis
```{r}
dat_fin <- dat3

# Contrast factor levels
dat_fin$LisCond <- as.factor(dat_fin$LisCond)
contrasts(dat_fin$LisCond)

dat_fin$Style <- as.factor(dat_fin$Style)
dat_fin$Style <- relevel(dat_fin$Style, "Conversational")
contrasts(dat_fin$Style)

dat_fin$Group <- as.factor(dat_fin$Group)
contrasts(dat_fin$Group)

# Log-transform and scale RTs
dat_fin$LogRT <- scale(log(dat_fin$RT))
```

# Run Bayesian mixed-effects logistic model
```{r}
# Set priors
priors <- c(
  set_prior("normal(0,10)", class = "Intercept"),
  set_prior("normal(0,10)", class = "b"),
  set_prior("normal(0,10)", class = "sd"),
  set_prior("lkj(2)", class = "cor")
  )
```

```{r eval=FALSE}
# Run analysis
bmix1 <- brm(Accuracy ~ Style*LisCond + LogRT + (1|Subject) + (Style*LisCond |AL_word) +
               (1 + Style |Partword),
             data = dat_fin, family = 'bernoulli',
             warmup = 1000, chains = 4, iter = 2000,
             prior = priors,
             sample_prior = TRUE,
             seed = 2020,
             control = list(adapt_delta = 0.99, max_treedepth = 15))
summary(bmix1)
```

```{r eval=FALSE}
# Include Group (monolingual vs. bilingual) as a factor
bmix2 <- brm(Accuracy ~ Style*LisCond*Group + LogRT + (1|Subject) + (Style*LisCond |AL_word) +
               (1 + Style |Partword),
             data = dat_fin, family = 'bernoulli',
             warmup = 1000, chains = 4, iter = 2000,
             prior = priors,
             sample_prior = TRUE,
             seed = 2020,
             control = list(adapt_delta = 0.99, max_treedepth = 15))
summary(bmix2)
```

# Results
## Get marginal posterior distributions of the parameter values
```{r}
mar_posterior <- as.matrix(bmix1)

# Get the marginal posteriors of the fixed-effect parameters only
fixed_posterior <- mar_posterior[,1:7]
fixed_posterior <- as.data.frame(fixed_posterior)

# Rename columns
names(fixed_posterior)[names(fixed_posterior) == "b_StyleClear:LisCondSNR_0"] <-
  "b_StyleClearXLisCondSNR_0"
names(fixed_posterior)[names(fixed_posterior) == "b_StyleClear:LisCondSNR_3"] <-
  "b_StyleClearXLisCondSNR_3"

# Plot marginal posteriors on all fixed-effect parameters using tidybayes
color_scheme_set("gray")
mar_posterior_fixed_plot <- fixed_posterior %>%
  select(starts_with("b")) %>%
  gather(Parameter, Value, b_Intercept:b_StyleClearXLisCondSNR_3) %>%
  ggplot(aes(y = Parameter, x = Value)) +
  stat_halfeyeh(point_interval = mean_qi, .width=0.95, normalize = "groups") +
  theme_classic() +
  geom_vline(xintercept = 0, linetype = "dashed", color = "black") +
  coord_cartesian(xlim = c(-3, 4)) +
  xlab("Parameter value") +
  ylab("") +
  scale_y_discrete(limits = c("b_LogRT", "b_StyleClearXLisCondSNR_0","b_StyleClearXLisCondSNR_3",
                              "b_LisCondSNR_0", "b_LisCondSNR_3", "b_StyleClear","b_Intercept"),
                     labels = c("b_LogRT" = expression(beta["LogRT"]),
                                "b_StyleClearXLisCondSNR_0" = expression(beta["Style × LisCond (0 dB SNR)"]),
                                "b_StyleClearXLisCondSNR_3" = expression(beta["Style × LisCond (+3 dB SNR)"]),
                                "b_LisCondSNR_0" = expression(beta["LisCond (0 dB SNR)"]),
                                "b_LisCondSNR_3" = expression(beta["LisCond (+3 dB SNR)"]),
                                "b_StyleClear" = expression(beta["Style"]),
                                "b_Intercept" = expression(beta["Intercept"]))) +
  theme(axis.title.x = element_text(size=12),
        axis.text.y = element_text(size=10, color="black"))
mar_posterior_fixed_plot

# Save graph
pdf("/Users/adamguo/Desktop/Fig_3.pdf", width = 6, height = 4) 
plot(mar_posterior_fixed_plot) 
dev.off()
```

## Calculate posterior distribution of accuracy for each condition
```{r}
# Caclulate log-odds ratio for each conditon
fixed_posterior$est_Quiet_conv <- fixed_posterior$b_Intercept
fixed_posterior$est_Quiet_clear <- fixed_posterior$b_Intercept + fixed_posterior$b_StyleClear
fixed_posterior$est_NM_0_conv <- fixed_posterior$b_Intercept + fixed_posterior$b_LisCondSNR_0
fixed_posterior$est_NM_0_clear <- fixed_posterior$b_Intercept + fixed_posterior$b_StyleClear + fixed_posterior$b_LisCondSNR_0 + fixed_posterior$b_StyleClearXLisCondSNR_0
fixed_posterior$est_NM_3_conv <- fixed_posterior$b_Intercept + fixed_posterior$b_LisCondSNR_3
fixed_posterior$est_NM_3_clear <- fixed_posterior$b_Intercept + fixed_posterior$b_StyleClear + fixed_posterior$b_LisCondSNR_3 + fixed_posterior$b_StyleClearXLisCondSNR_3

## Calculate accuracy for each condition
fixed_posterior$acc_Quiet_conv <- plogis(fixed_posterior$est_Quiet_conv)
fixed_posterior$acc_Quiet_clear <- plogis(fixed_posterior$est_Quiet_clear)
fixed_posterior$acc_NM_0_conv <- plogis(fixed_posterior$est_NM_0_conv)
fixed_posterior$acc_NM_0_clear <- plogis(fixed_posterior$est_NM_0_clear)
fixed_posterior$acc_NM_3_conv <- plogis(fixed_posterior$est_NM_3_conv)
fixed_posterior$acc_NM_3_clear <- plogis(fixed_posterior$est_NM_3_clear)
```

## Calculate the posterior distributions of accuracy drop from the quiet condition
```{r}
# Calculate posterior accuracy drop from the quiet condition for each style
fixed_posterior$drop_NM_3_clear <- fixed_posterior$acc_NM_3_clear - fixed_posterior$acc_Quiet_clear
fixed_posterior$drop_NM_0_clear <- fixed_posterior$acc_NM_0_clear - fixed_posterior$acc_Quiet_clear

fixed_posterior$drop_NM_3_conv <- fixed_posterior$acc_NM_3_conv - fixed_posterior$acc_Quiet_conv
fixed_posterior$drop_NM_0_conv <- fixed_posterior$acc_NM_0_conv - fixed_posterior$acc_Quiet_conv

# Drop difference across styles for NM 3
fixed_posterior$drop_NM_3_clear_conv_diff <- fixed_posterior$drop_NM_3_clear - fixed_posterior$drop_NM_3_conv

# Drop difference across styles for NM 0
fixed_posterior$drop_NM_0_clear_conv_diff <- fixed_posterior$drop_NM_0_clear - fixed_posterior$drop_NM_0_conv

# Means and 95% credivle intervals (%)

## Clear in noise at +3 dB SNR
mean(fixed_posterior$drop_NM_3_clear) * 100
quantile(fixed_posterior$drop_NM_3_clear, probs = c(0.025, 0.975)) * 100

## Clear in noise at 0 dB SNR
mean(fixed_posterior$drop_NM_0_clear) * 100
quantile(fixed_posterior$drop_NM_0_clear, probs = c(0.025, 0.975)) * 100

## Conversational in noise at +3 dB SNR
mean(fixed_posterior$drop_NM_3_conv) * 100
quantile(fixed_posterior$drop_NM_3_conv, probs = c(0.025, 0.975)) * 100

## Conversational in noise at 0 dB SNR
mean(fixed_posterior$drop_NM_0_conv) * 100
quantile(fixed_posterior$drop_NM_0_conv, probs = c(0.025, 0.975)) * 100

## Drop difference across style (NM 3)
mean(fixed_posterior$drop_NM_3_clear_conv_diff) * 100
quantile(fixed_posterior$drop_NM_3_clear_conv_diff, probs = c(0.025, 0.975)) * 100

## Prob. that the reduction is greater for clear style (NM 3)
sum(fixed_posterior$drop_NM_3_clear_conv_diff < 0) / length(fixed_posterior$drop_NM_3_clear_conv_diff)

## Drop difference across style (NM 0)
mean(fixed_posterior$drop_NM_0_clear_conv_diff) * 100
quantile(fixed_posterior$drop_NM_0_clear_conv_diff, probs = c(0.025, 0.975)) * 100

## Prob. that the reduction is greater for clear style (NM 0)
sum(fixed_posterior$drop_NM_0_clear_conv_diff < 0) / length(fixed_posterior$drop_NM_0_clear_conv_diff)
```

## Calculate the posterior distributions of clear speech benefit
```{r}
# Calculate posterior clear speech benefit for each level of the LisCond factor
fixed_posterior$csb_Quiet <- fixed_posterior$acc_Quiet_clear - fixed_posterior$acc_Quiet_conv
fixed_posterior$csb_NM_0 <- fixed_posterior$acc_NM_0_clear - fixed_posterior$acc_NM_0_conv
fixed_posterior$csb_NM_3 <- fixed_posterior$acc_NM_3_clear - fixed_posterior$acc_NM_3_conv

# Convert to percentages
fixed_posterior$csb_Quiet_per <- fixed_posterior$csb_Quiet * 100
fixed_posterior$csb_NM_0_per <- fixed_posterior$csb_NM_0 * 100
fixed_posterior$csb_NM_3_per <- fixed_posterior$csb_NM_3 * 100

# Computer clear speech benefit difference (%) between the two noist conditions
fixed_posterior$csb_NM_0_3_per_diff <- fixed_posterior$csb_NM_0_per - fixed_posterior$csb_NM_3_per

# Mean and 95% credivle intervals (%)

## Quiet
mean(fixed_posterior$csb_Quiet_per)
quantile(fixed_posterior$csb_Quiet_per, probs = c(0.025, 0.975))

table(fixed_posterior$csb_Quiet_per <= 0)[2]/4000 ## Probablity that clear speech benefit is zero or below

## In noise at +3 dB SNR
mean(fixed_posterior$csb_NM_3_per)
quantile(fixed_posterior$csb_NM_3_per, probs = c(0.025, 0.975))

## In noise at 0 dB SNR
mean(fixed_posterior$csb_NM_0_per)
quantile(fixed_posterior$csb_NM_0_per, probs = c(0.025, 0.975))

## Difference between 0 dB and +3 dB SNR in clear speech benefit
mean(fixed_posterior$csb_NM_0_3_per_diff)
quantile(fixed_posterior$csb_NM_0_3_per_diff, probs = c(0.025, 0.975))

# Plot posterior distributions of clear speech benefit using tudybayes
color_scheme_set("gray")
posterior_csb_plot <- fixed_posterior %>%
  select(ends_with("per")) %>%
  gather(Parameter, Value, csb_Quiet_per:csb_NM_3_per) %>%
  ggplot(aes(y = Parameter, x = Value)) +
  stat_halfeyeh(point_interval = mean_qi, .width = 0.95) +
  theme_classic() +
  geom_vline(xintercept = 0, linetype = "dashed", color = "black") +
  coord_cartesian(xlim = c(-25, 25)) +
  xlab("Clear speech benefit (%)") +
  ylab("") +
  scale_y_discrete(limits = c("csb_NM_0_per","csb_NM_3_per","csb_Quiet_per"),
                      labels = c("csb_NM_0_per" = "Noise-masked\n(0 dB SNR)",
                                 "csb_NM_3_per" = "Noise-masked\n(+3 dB SNR)",
                                 "csb_Quiet_per" = "Quiet")) +
  theme(axis.title.x = element_text(size = 12),
        axis.text.y = element_text(size = 10, color = "black"))

posterior_csb_plot
pdf("/Users/adamguo/Desktop/Fig_4.pdf", width = 6, height = 4)
plot(posterior_csb_plot)
dev.off()
```

# Boxplot (Figure 2)
```{r}
# Prepare data for plotting
fig_dat <- aggregate(Accuracy ~ Subject + Condition + Style + LisCond, dat_fin, mean)

# Calculate no. of observations of the conditions
# no_NO <- xtabs(~Condition, dat_fin)
# no_NO <- as.data.frame(no_NO)
# no_NO <- no_NO[no_NO$Freq != 0,]

# Calculate SE for the conditions
condMeans <- aggregate(Accuracy ~ Condition, dat_fin, mean)
# MeanSE_NO$SE <- sqrt(MeanSE_NO$Accuracy * (1 - MeanSE_NO$Accuracy) / no_NO$Freq)

# Add condition means to the data frame for plotting
fig_dat$Mean = 0
fig_dat[fig_dat$Condition == "Quiet_clear",]$Mean <-
  condMeans[condMeans$Condition == "Quiet_clear",]$Accuracy
fig_dat[fig_dat$Condition == "Quiet_conv",]$Mean <-
  condMeans[condMeans$Condition == "Quiet_conv",]$Accuracy

fig_dat[fig_dat$Condition == "NM_0_clear",]$Mean <-
  condMeans[condMeans$Condition == "NM_0_clear",]$Accuracy
fig_dat[fig_dat$Condition == "NM_0_conv",]$Mean <-
  condMeans[condMeans$Condition == "NM_0_conv",]$Accuracy

fig_dat[fig_dat$Condition == "NM_3_clear",]$Mean <-
  condMeans[condMeans$Condition == "NM_3_clear",]$Accuracy
fig_dat[fig_dat$Condition == "NM_3_conv",]$Mean <-
  condMeans[condMeans$Condition == "NM_3_conv",]$Accuracy

# Order levels of Style and LisCond
fig_dat$Style <- factor(fig_dat$Style, levels = c("Conversational", "Clear"))
fig_dat$LisCond <- factor(fig_dat$LisCond, levels = c("Quiet", "SNR_3", "SNR_0"))

# Now create the boxplot
pd1 <- position_dodge(0.16)
pd2 <- position_dodge(1.2)

boxplot_fig <- ggplot(fig_dat) +
  aes(x = LisCond, y = Accuracy * 100, color = Style, fill = Style, shape = Style) +
  geom_beeswarm(cex = 1.5, size = 2.0, dodge.width = 1.0) +
  stat_boxplot(geom = "errorbar", position = pd1, color = "black", width = 0.15) +
  geom_boxplot(width = 0.15, position = pd1, color = "black", outlier.shape = NA) + 
  geom_label(stat = 'summary', fun = mean, aes(label = round(..y.., 0)),
                 color = "black", fill = "white", position = position_dodge(0.53), size = 3.5, alpha = 0.4) +
  scale_fill_manual(values = c("#C0C0C0", "#5d5d5d")) +
  scale_color_manual(values=  c("#C0C0C0", "#5d5d5d")) +
  scale_x_discrete(labels = c("Quiet" = "Quiet",
                              "SNR_3" = "Noise-masked\n(+3 dB SNR)",
                              "SNR_0" = "Noise-masked\n(0 dB SNR)")) +
  theme_classic() +
  ggtitle("") +
  xlab("") +
  ylab("% Correct") + 
  theme(text = element_text(size = 18),
        legend.text = element_text(size = 14),
        legend.title = element_text(size = 14),
        legend.position = c(0.2, 0.2),
        legend.background = element_blank(),
        plot.title = element_text(hjust = 0.70, face = "bold", size = 20),
        axis.title = element_text(size = 20))
boxplot_fig

pdf("/Users/adamguo/Desktop/Fig_2.pdf", width = 10, height = 5) 
plot(boxplot_fig)
dev.off()
```

# Sensitivity analysis
```{r}
# Set priors with different degrees of uncertainty for fixed effectss
priors_sa_1 <- c(
  set_prior("normal(0,0.1)", class = "Intercept"),
  set_prior("normal(0,0.1)", class = "b"),
  set_prior("normal(0,10)", class = "sd"),
  set_prior("lkj(2)", class = "cor")
  )

priors_sa_2 <- c(
  set_prior("normal(0,1)", class = "Intercept"),
  set_prior("normal(0,1)", class = "b"),
  set_prior("normal(0,10)", class = "sd"),
  set_prior("lkj(2)", class = "cor")
  )

priors_sa_3 <- c(
  set_prior("normal(0,25)", class = "Intercept"),
  set_prior("normal(0,25)", class = "b"),
  set_prior("normal(0,10)", class = "sd"),
  set_prior("lkj(2)", class = "cor")
  )

priors_sa_4 <- c(
  set_prior("normal(0,50)", class = "Intercept"),
  set_prior("normal(0,50)", class = "b"),
  set_prior("normal(0,10)", class = "sd"),
  set_prior("lkj(2)", class = "cor")
  )
```

```{r}
# Define a function for running the model
run_bmix_sa <- function(priors_sa) {
  bmix_sa <- brm(Accuracy ~ Style*LisCond + LogRT + (1|Subject) + (Style*LisCond |AL_word) +
                   (1 + Style |Partword),
                 data = dat_fin, family = 'bernoulli',
                 warmup = 1000, chains = 4, iter = 2000,
                 prior = priors_sa,
                 sample_prior = TRUE,
                 seed = 2020,
                 control = list(adapt_delta = 0.99, max_treedepth = 15))
  return(bmix_sa)
}
```

```{r eval=FALSE}
# Run models
bmix_sa_1 <- run_bmix_sa(priors_sa_1)
bmix_sa_2 <- run_bmix_sa(priors_sa_2)
bmix_sa_3 <- run_bmix_sa(priors_sa_3)
bmix_sa_4 <- run_bmix_sa(priors_sa_4)
```

```{r}
# Define a function for getting posteriors as done for bmix1
get_posteriors <- function(bmix_sa) {
  mar_posterior_sa <- as.matrix(bmix_sa)
  
  # Get the marginal posteriors of the fixed-effect parameters only
  fixed_posterior_sa <- mar_posterior_sa[,1:7]
  fixed_posterior_sa <- as.data.frame(fixed_posterior_sa)
  
  # Rename columns
  names(fixed_posterior_sa)[names(fixed_posterior_sa) == "b_StyleClear:LisCondSNR_0"] <-
  "b_StyleClearXLisCondSNR_0"
  names(fixed_posterior_sa)[names(fixed_posterior_sa) == "b_StyleClear:LisCondSNR_3"] <-
  "b_StyleClearXLisCondSNR_3"
  
  # Caclulate log-odds ratio for each conditon
  fixed_posterior_sa$est_Quiet_conv <- fixed_posterior_sa$b_Intercept
  fixed_posterior_sa$est_Quiet_clear <- fixed_posterior_sa$b_Intercept + fixed_posterior_sa$b_StyleClear
  fixed_posterior_sa$est_NM_0_conv <- fixed_posterior_sa$b_Intercept + fixed_posterior_sa$b_LisCondSNR_0
  fixed_posterior_sa$est_NM_0_clear <- fixed_posterior_sa$b_Intercept + fixed_posterior_sa$b_StyleClear +
    fixed_posterior_sa$b_LisCondSNR_0 + fixed_posterior_sa$b_StyleClearXLisCondSNR_0
  fixed_posterior_sa$est_NM_3_conv <- fixed_posterior_sa$b_Intercept + fixed_posterior_sa$b_LisCondSNR_3
  fixed_posterior_sa$est_NM_3_clear <- fixed_posterior_sa$b_Intercept + fixed_posterior_sa$b_StyleClear +
    fixed_posterior_sa$b_LisCondSNR_3 + fixed_posterior_sa$b_StyleClearXLisCondSNR_3
  
  # Calculate accuracy for each condition
  fixed_posterior_sa$acc_Quiet_conv <- plogis(fixed_posterior_sa$est_Quiet_conv)
  fixed_posterior_sa$acc_Quiet_clear <- plogis(fixed_posterior_sa$est_Quiet_clear)
  fixed_posterior_sa$acc_NM_0_conv <- plogis(fixed_posterior_sa$est_NM_0_conv)
  fixed_posterior_sa$acc_NM_0_clear <- plogis(fixed_posterior_sa$est_NM_0_clear)
  fixed_posterior_sa$acc_NM_3_conv <- plogis(fixed_posterior_sa$est_NM_3_conv)
  fixed_posterior_sa$acc_NM_3_clear <- plogis(fixed_posterior_sa$est_NM_3_clear)
  
  # Calculate posterior clear speech benefit for each level of the LisCond factor
  fixed_posterior_sa$csb_Quiet <- fixed_posterior_sa$acc_Quiet_clear - fixed_posterior_sa$acc_Quiet_conv
  fixed_posterior_sa$csb_NM_0 <- fixed_posterior_sa$acc_NM_0_clear - fixed_posterior_sa$acc_NM_0_conv
  fixed_posterior_sa$csb_NM_3 <- fixed_posterior_sa$acc_NM_3_clear - fixed_posterior_sa$acc_NM_3_conv
  
  # Convert to percentages
  fixed_posterior_sa$csb_Quiet_per <- fixed_posterior_sa$csb_Quiet * 100
  fixed_posterior_sa$csb_NM_0_per <- fixed_posterior_sa$csb_NM_0 * 100
  fixed_posterior_sa$csb_NM_3_per <- fixed_posterior_sa$csb_NM_3 * 100
  
  # Calculate posterior accuracy drop from the quiet condition for each style
  fixed_posterior_sa$drop_NM_3_clear <- fixed_posterior_sa$acc_NM_3_clear -
    fixed_posterior_sa$acc_Quiet_clear
  fixed_posterior_sa$drop_NM_0_clear <- fixed_posterior_sa$acc_NM_0_clear -
    fixed_posterior_sa$acc_Quiet_clear
  fixed_posterior_sa$drop_NM_3_conv <- fixed_posterior_sa$acc_NM_3_conv -
    fixed_posterior_sa$acc_Quiet_conv
  fixed_posterior_sa$drop_NM_0_conv <- fixed_posterior_sa$acc_NM_0_conv -
    fixed_posterior_sa$acc_Quiet_conv
  
  return(fixed_posterior_sa)
}
```

```{r}
# Get posteriors for the 4 models
fixed_posterior_sa_1 <- get_posteriors(bmix_sa_1)
fixed_posterior_sa_2 <- get_posteriors(bmix_sa_2)
fixed_posterior_sa_3 <- get_posteriors(bmix_sa_3)
fixed_posterior_sa_4 <- get_posteriors(bmix_sa_4)
```

```{r}
# Get a dataframe containing posteriors of clear speech benefit of different models
sa_data_csb_quiet <- cbind(c(rep("Normal(0, 0.1)", 4000),
                   rep("Normal(0, 1)", 4000),
                   rep("Normal(0, 10)", 4000),
                   rep("Normal(0, 25)", 4000),
                   rep("Normal(0, 50)", 4000)),
                 rbind(fixed_posterior_sa_1["csb_Quiet_per"],
                       fixed_posterior_sa_2["csb_Quiet_per"],
                       fixed_posterior["csb_Quiet_per"], # The model reported in the paper
                       fixed_posterior_sa_3["csb_Quiet_per"],
                       fixed_posterior_sa_4["csb_Quiet_per"]))
```

```{r}
# Rename the column specifying the prior used (as Prior), factorize Prior, and relevel it
sa_data_csb_quiet <- sa_data_csb_quiet %>%
  rename(Prior = 1) %>%
  mutate(Prior = factor(Prior, levels = c("Normal(0, 0.1)",
                                          "Normal(0, 1)",
                                          "Normal(0, 10)",
                                          "Normal(0, 25)",
                                          "Normal(0, 50)")))
```

```{r}
# 95% CIs of clear speech benefit in quiet
quantile(sa_data_csb_quiet[sa_data_csb_quiet$Prior == "Normal(0, 0.1)",]$csb_Quiet_per,
         probs = c(0.025, 0.975))
quantile(sa_data_csb_quiet[sa_data_csb_quiet$Prior == "Normal(0, 1)",]$csb_Quiet_per,
         probs = c(0.025, 0.975))
quantile(sa_data_csb_quiet[sa_data_csb_quiet$Prior == "Normal(0, 25)",]$csb_Quiet_per,
         probs = c(0.025, 0.975))
quantile(sa_data_csb_quiet[sa_data_csb_quiet$Prior == "Normal(0, 50)",]$csb_Quiet_per,
         probs = c(0.025, 0.975))
```

```{r}
sa_csb_quiet_plot <- sa_data_csb_quiet %>%
  ggplot(aes(y = Prior, x = csb_Quiet_per)) +
  stat_halfeyeh(point_interval = mean_qi, .width = 0.95) +
  theme_classic() +
  geom_vline(xintercept = 0, linetype = "dashed", color = "black") +
  xlab("Clear speech benefit (%) in quiet ") +
  ylab("") +
  coord_flip(xlim = c(-20, 30)) +
  theme(axis.text.x = element_text(size = 12),
        axis.title.y = element_text(size = 14))
sa_csb_quiet_plot
```

```{r}
# Save the plot
pdf("/Users/adamguo/Desktop/SA_plot.pdf", width = 8, height = 4) 
plot(sa_csb_quiet_plot)
dev.off()
```

# Save all the objects created
```{r}
save.image(file = "all_objects.RData") 
```
